\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{courier}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{microtype}
%\usepackage[T1]{fontenc}
%\renewcommand\tabularxcolumn[1]{m{#1}}% vertically center
\newcolumntype{Y}{>{\raggedright\arraybackslash}X} % A regular tabularx column but left justified instead of full justified.
% -------------------------------------------------------
% FROM https://tex.stackexchange.com/questions/348651/c-code-to-add-in-the-document
\usepackage{listings}
\usepackage{xcolor}
\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{CStyle}{
    commentstyle=\color{mGreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{mGray},
    stringstyle=\color{mPurple},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,       
    keepspaces=true,                 
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}

\lstset{style=CStyle}
% -------------------------------------------------------
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\title{Toybox Bug Analysis}
\begin{document}
\maketitle

\begin{tabularx}{\textwidth}{rY}
\toprule
File & lsm.h \\
Line & 63 \\
Description & Uninitialized variable: result \\
Number of Configurations & 432\footnote{The actual cppcheck bug reports listed various C source code files which included this header as the source of the bug, even though \texttt{lsm.h} was the actual source. This is the number of total occurrences of the bug across multiple files.}\\
\midrule
\multicolumn{2}{c}{Code Sample} \\
\multicolumn{2}{c}{\lstinputlisting{code/lsm_h_lsm_context.c}} \\
\midrule
Status & False positive. \\
Remarks & In configurations including \texttt{TOYBOX\_SMACK} and \texttt{TOYBOX\_SELINUX} \texttt{smack\_new\_label\_from\_self} and \texttt{getcon} are replaced with the value -1, respectively. In other configurations, \texttt{*result} is an out parameter. \\
\bottomrule
\end{tabularx}

\begin{tabularx}{\textwidth}{rY}
\toprule
File & base64.c\\
Line & 35\\
Description & Expression \texttt{`this.base64.columns\&\&++*x == this.base64.columns'} \\ & depends on order of evaluation of side effects. \\
Number of Configurations & 478 \\
\midrule
\multicolumn{2}{c}{Code Sample} \\
\multicolumn{2}{c}{\lstinputlisting[firstline=31,lastline=39]{code/base64.c}} \\
\midrule
Status & False positive. \\
Remarks & Although \texttt{TT.columns} appears twice in the same expression, it is modified neither time. Thus, the order of evaluation of side effects does not matter. \\
\bottomrule
\end{tabularx}

\end{document}