\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{courier}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{microtype}
%\usepackage[T1]{fontenc}
%\renewcommand\tabularxcolumn[1]{m{#1}}% vertically center
\newcolumntype{Y}{>{\raggedright\arraybackslash}X} % A regular tabularx column but left justified instead of full justified.
% -------------------------------------------------------
% FROM https://tex.stackexchange.com/questions/348651/c-code-to-add-in-the-document
\usepackage{listings}
\usepackage{xcolor}
\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{CStyle}{
    commentstyle=\color{mGreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{mGray},
    stringstyle=\color{mPurple},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,       
    keepspaces=true,
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}

\lstset{style=CStyle}
% -------------------------------------------------------
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

% BUG REPORT TEMPLATE -----------------------------------
%\begin{tabularx}{\textwidth}{rY}
%\toprule
%File & •\\
%Line & •\\
%Description & •\\
%Number of Configurations & •\\
%\midrule
%\multicolumn{2}{c}{Code Sample} \\
%\multicolumn{2}{l}{\lstinputlisting{code/•}} \\
%\midrule
%Status & •\\
%Remarks & •\\
%\bottomrule
%\end{tabularx}
% -------------------------------------------------------
\title{Static Analysis Preliminary Tool Investigation}
\begin{document}
\maketitle

\section{\textcolor{green}{CBMC}}

Tool available and runnable. Model checker that verifies properties
such as pointers and array bounds. It works by translating the program
into a formula. 

Download: http://www.cprover.org/cbmc/

Manual: http://www.cprover.org/cprover-manual/cbmc.html

\section{\textcolor{green}{clang-scan-build}}

Tool available and runnable. Clang can analyze individual C file or
the complete codebase built with make/xcodebuild.

Download: https://clang-analyzer.llvm.org

Manual: https://clang-analyzer.llvm.org/scan-build

\section{\textcolor{orange}{clang-tidy}}

Need to further check how relevant the bugs are.

Manual: http://clang.llvm.org/extra/clang-tidy/

\section{\textcolor{red}{CMetrics}}

Code metrics tool; does not report bugs.

\section{\textcolor{green}{CodeSonar}}

GrammaTech static analysis tool. Can submit a request to obtain 30-day trial.
Can also apply for its free academic program (submitted).

Website: https://www.grammatech.com/products/codesonar

\section{\textcolor{orange}{Corrode}}

C to Rust translator. Not fully automatic. Can then run Rust compiler to catch bugs.

Code repo: https://github.com/jameysharp/corrode

\section{\textcolor{green}{cppcheck}}

Already included.

\section{\textcolor{orange}{CppDepend}}

Commercial tool. Can obtain 30-day trial version. Detect dependency and
structural flaws. Does not seem very relevant.

Website: https://www.cppdepend.com

\section{\textcolor{red}{cpplint}}

C++ code style checker.

\section{\textcolor{red}{cqmetrics}}

Code metrics tool; does not report bugs.

\section{\textcolor{red}{CScout}}

C refactoring tool; does not report bugs.

\section{\textcolor{orange}{flawfinder}}

Security bugs found are important. Difficult to obtain the tool. Pre-package versions
are out-dated. Need to build from source.

Website: https://www.dwheeler.com/flawfinder/

\section{\textcolor{orange}{Flint++}}

C++ linter. Errors reported are not very interesting.

Code repo: https://github.com/JossWhittle/FlintPlusPlus



\end{document}